A Logistic Regression Approach to CoIL Challenge 2000

### 2019-12-13 final project/Manuscript.Rmd
Added more to methodology and appendix

@@

>>>>

The MOSTYPE variable has 40 customer types.  Not all customer types were statiscally significant predictors.  We identified those with a probability greater than 0.5 to purchase the insurance product as the `LIKELY_CUSTOMER` variable.  Our second model used LIKELY_CUSTOMER and PPERSAUT.

@@

## Probability of Purchasing Product (in blue) by Customer Type

```{r, echo=FALSE, fig.width=10, fig.height=11}
temp <- up_train %>%
  group_by(MOSTYPE) %>%
  tally() %>%
  rename(total = n)

temp <- up_train %>%
  filter(CARAVAN == 1) %>%
  group_by(MOSTYPE) %>%
  tally() %>%
  merge(temp, ., all.x = TRUE) %>%
  mutate(share_1 = ifelse(is.na(n), 0, n / total)) %>%
  mutate(order = row_number(share_1)) %>%
  select(-n) %>%
  merge(temp)

temp <- up_train %>%
  group_by(CARAVAN, MOSTYPE) %>%
  tally() %>%
  merge(temp) %>%
  mutate(share = n / total)

ggplot(temp, aes(x = reorder(MOSTYPE, order), y = share, fill = CARAVAN))+
  geom_bar(stat="identity") +
  scale_fill_brewer(palette = "Set1") +
  coord_flip() +
  xlab(element_blank()) +
  ylab(element_blank()) +
  geom_hline(yintercept = 0.5, color = "white", linetype = "dashed") +
  theme_minimal() +
  theme(legend.position = "none") 
```
